Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2022-04-21 paper/manuscript.Rmd
Stupid linebreak things

Code for the analyses in this chapter is archived on Zenodo at \<[[DOI:10.5281/zenodo.5514335\\\\](DOI:10.5281/zenodo.5514335\){.uri}]([DOI:10.5281/zenodo.5514335\\](DOI:10.5281/zenodo.5514335)%7B.uri%7D){.uri}\> [\@norman_karinormanbiodivts_2021]. Data products are on Github at <https://github.com/karinorman/biodivTS_data>. Original data sources are open access and available at their respective providers.

>>>>

Code for the analyses in this chapter is archived on Zenodo at \<[[DOI:10.5281/zenodo.5514335\\\\](DOI:10.5281/zenodo.5514335){.uri}](%5BDOI:10.5281/zenodo.5514335\%5D(DOI:10.5281/zenodo.5514335)%7B.uri%7D){.uri}\> [\@norman_karinormanbiodivts_2021].
Data products are on Github at <https://github.com/karinorman/biodivTS_data>.
Original data sources are open access and available at their respective providers.
